Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-31 documentation/paper.tex
Added cuts for basic quality and bubble multiplicity

>>>>

\section{Data Cuts}

Techniques in this study are trained and validated on a number of different data sets. The selection of these sets focused on the fundamental trade-off between quality and quantity of data; by setting a higher standard for the validity of training data, one has less data to train on.

The initial data set $D$ to which these cuts are applied consists of all events recorded during PICO-60 run 2.

\subsection{Basic Quality Cut}

A certain number of cuts are necessarily applied to all data to ensure meaningful results. Otherwise, significant overfitting on biases in the data is likely. This basic quality cut $QualCut(D)$ consists of the following restrictions:
\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated ($[X, Y, Z]\neq[-100, -100, -100]$)
\end{itemize}

\subsection{Bubble Multiplicity Cut}

PICO-60 events which include multiple bubbles are \textit{always} neutron events; alpha particles and WIMP candidates never scatter. Thus, no discriminator is required to handle these events, so they are removed. The bubble multiplicity cut $MultiCut(D)$ consists of the following restrictions:
\begin{itemize}
    \item Either 0 or 1 bubbles are detected based on images from the camera ($\texttt{nbub}<2$)
    \item The number of bubbles approximated using the pressure transducer is close to 1 ($0.7<\texttt{dytranCZ}<1.3$)
\end{itemize}
